---
title: "Browsing the elements of the object"
shorttitle: "Most important methods"
author: "Lorena Pantano"
date: "`r BiocStyle::doc_date()`"
package: "`r BiocStyle::pkg_ver('bcbioSmallRna')`"
abstract: >
  bcbioSmallRna package version: `r packageVersion("bcbioSmallRna")`
output:
  rmarkdown::html_document:
    highlight: pygments
    toc: true
    fig_width: 5
vignette: >
  %\VignetteIndexEntry{Browsing the elements of the object}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding[utf8]{inputenc}
  %\VignetteKeywords{Quality Control, Visualization, smallRNASeq, ReportWriting}
---

```{r aes, results='hide'}
library(BiocStyle)
knitr::opts_chunk$set(tidy=FALSE,
                      dev="png",
                      message=FALSE, error=FALSE,
                      warning=TRUE)
library(knitr)
library(ggplot2)

# Set seed for reproducibility
set.seed(1454944673L)

theme_set(
    theme_light(base_size = 11L))
theme_update(
    legend.justification = "center",
    legend.position = "bottom")
```

```{r setup, message=FALSE}
library(isomiRs)
library(DEGreport)
library(bcbioSmallRna)

data(sbcb)
# bcbioSmallRnaDataSet
bcb <- sbcb
```

# Get count matrix

You can get all the count matrix with the method `mirna`, `isomir`, `cluster`:

```{r counts}
# for miRNAs
head(mirna(bcb))
# for clusters
head(cluster(bcb))
# for isomir
head(isomir(bcb))
```

By default this is the raw count data, however you can access a pre-computed
normalized data using the second positional parameter `log`:
 
```{r normalized}
head(mirna(bcb, "log"))
```

# Metrics

There are some important metris stored in the object that can be gotten with
the following methods:
 
## Adapter removal

These section shows how to get general stats for the adapter removal step.

To get the numbers of adapters removed at each position:

```{r adapter-by-position}
head(adapter(bcb)[["reads_by_pos"]])
```

As well, the total reads with adapter can be seen with:

```{r adapter-total}
adapter(bcb)[["reads_by_sample"]]
```

## General metrics

All the metrics performed by bcbio can be seen with:

```{r all-metrics}
metrics(bcb)
```


# Session 

```{r, results='markup'}
sessionInfo()
```

